The development of infants' responses to mispronunciations: A Meta-Analysis

### 2019-05-06 VonHolzenBergmann_MPMetaAnalysis.tex
begin Monster paper transformation

Acquiring a first language means that young learners are solving a host
of tasks in a short amount of time. As infants develop into toddlers
during their second and third years they learn new words in earnest
while simultaneously refining their knowledge about the sounds that make
up these words (Best, 1994, 1995; Curtin \& Werker, 2007; Kuhl, 2004;
Werker \& Curtin, 2005). In a mature phono-lexical system, word
recognition must balance flexibility to slight variation (e.g., speaker
identity, accented speech) while distinguishing between phonetic details
that differentiate words in a given language (e.g.~cat-hat). To build
robust language knowledge, it seems useful to acquire this ability early
during development. Indeed, before children can correctly pronounce a
word, they already are aware that slight phonological deviations might
signal a change in word meaning (H. H. Clark \& Clark, 1977). This
mispronunciation sensitivity reflects the specificity with which infants
represent the phonological information of familiar words. As infants
continue to develop into expert language users, their language
processing matures and becomes more efficient, including their knowledge
of what constitutes a permissible versus word-changing phonological
deviation. In this paper, we aggregate and analyze the nearly 20 years
of literature investigating mispronunciation sensitivity in infants in
an attempt to uncover its characteristics and the trajectory of its
development.

@@

The study of Swingley and Aslin (2000) as well as subsequent studies
examining mispronunciation sensitivity address two complementary
principles that infants must discover in early phonological development
in order to form adult-like word representations and processing
capabilities: \emph{phonological constancy} and \emph{phonological
distinctiveness}. Phonological constancy is the ability to resolve
phonological variation across different instances of a word, as long as
the variation does not compromise the overall identity of the word. For
example, different speakers - particularly across genders and accents -
produce the same word with notable acoustic variation, although the word
remains the same. In contrast, phonological distinctiveness describes
the ability to differentiate between different words that happen to be
phonologically similar, such as bad/bed or cat/hat. To successfully
recognize words, speakers of a given language must therefore
simultaneously use both phonological constancy and distinctiveness to
determine where phonological variation is appropriate and where it
changes a word's meaning. Both abilities have to be acquired, because
language systems differ in which sounds signal a meaning change.

In the current study, we focus on infants' developing ability to
correctly apply the principles of phonological constancy and
distinctiveness by using a meta-analytic approach to investigate
mispronunciation sensitivity. Considering that infants are sensitive to
mispronunciations and that, in general, their processing matures with
development, we examine the shape of mispronunciation sensitivity over
the course of the second and third year. There are three distinct
possibilities how mispronunciation sensitivity might change as infants
become native speakers, which are all respectively supported by single
studies and additionally two possibilities are predicted by key
theoretical accounts. By aggregating all publicly available evidence
using meta-analysis, we can examine developmental trends making use of
data from a much larger and diverse sample of infants than is possible
in most single studies ({[}see Frank et al. (2017); for a notable
exception). Before we outline the meta-analytical approach and its
advantages in detail, we first discuss the proposals this study seeks to
disentangle and the data supporting each of the accounts.

Young infants may begin cautiously in their approach to word
recognition, rejecting any phonological variation in familiar words and
only later learning to accept appropriate variability. According to the
Perceptual Attunement account, this describes a shift away from specific
native phonetic patterns to a more mature understanding of the abstract
phonological structure of words (Best, 1994, 1995). This shift is
predicted to coincide with the vocabulary spurt around 18 months,
because it is causally related to vocabulary growth. In this case, we
would expect the size of mispronunciation sensitivity to be larger at
younger ages and \emph{decrease} as the child matures and learn more
words, although children continue to detect mispronunciations. Indeed,
young infants are more perturbed by accented speakers than older infants
in their recognition of familiar words (Best, Tyler, Gooding, Orlando,
\& Quann, 2009; Mulak, Best, Tyler, Kitamura, \& Irwin, 2014) or
learning of new words (Schmale, Hollich, \& Seidl, 2011).

According to a different theoretical framework, young infants may
instead begin with phonologically broad representations for familiar
words and only refine their representations as language experience
accumulates. PRIMIR (Processing Rich Information from Multidimensional
Interactive Representations; Curtin \& Werker, 2007; Curtin,
Byers-Heinlein, \& Werker, 2011; Werker \& Curtin, 2005) describes the
development of phonemic categories emerging as the number of word
form-meaning linkages increases. Vocabulary growth, therefore, promotes
more detailed phonological representations in familiar words. Following
this account, we predict an \emph{increase} in mispronunciation
sensitivity as infants mature and add more words to their growing
lexicon.

Finally, sensitivity to mispronunciation may not be modulated by
development at all. Infants' overall language processing becomes more
efficient, but their sensitivity to mispronunciations may not change.
Across infancy and toddlerhood, mispronunciations would thus be detected
and lead to less looks at a target than correct pronunciations, but the
size of this effect would not change, nor be related to vocabulary size.
This pattern is not predicted by any mainstream theory of language
acquisition, but for completeness we mention it here.

Research following the seminal study by Swingley and Aslin (2000) has
extended mispronunciation sensitivity to infants as young as 9 months
(Bergelson \& Swingley, 2017), indicating that from early stages of the
developing lexicon onwards, infants can and do detect mispronunciations.
Regarding the change in mispronunciation sensitivity over development,
however, only about half of studies have compared more than one age
group on the same mispronunciation task (see Table 1). In those single
studies all possible patterns of development lined out above have been
reported, making the current meta-analysis very informative.

One study has found evidence for infants to become \emph{less} sensitive
to mispronunciations as they develop. Mani and Plunkett (2011) presented
18- and 24-month-olds with mispronunciations varying in the number of
phonological features changed (e.g., changing an p into a b, a 1-feature
change, versus changing a p into a g, a 2-feature change). 18-month-olds
were sensitive to mispronunciations, regardless of the number of
features changed. 24-month-olds, in contrast, fixated the target image
equally for both correct and 1-feature mispronounced trials, although
they were sensitive to larger mispronunciations. In other words, for
1-feature mispronunciations at least, sensitivity decreased from 18 to
24 months, providing support to the prediction that mispronunciation
sensitivity may decrease with development.

In contrast, other studies have found evidence for \emph{greater}
mispronunciation sensitivity as children develop. More precisely, the
difference in target looking for correct and mispronounced trials is
reported to be smaller in younger infants and grows as infants develop.
Mani and Plunkett (2007) tested 15-, 18-, and 24-month-olds learning
British English; although all three groups were sensitive to
mispronunciations, 15-month-olds showed a less robust sensitivity. An
increase in sensitivity to mispronunciations has also been found from 20
to 24 months (Feest \& Fikkert, 2015) and 15 to 18 months
(Altvater-Mackensen, Feest, \& Fikkert, 2014) in Dutch infants, as well
as German infants from 22 to 25 months (Altvater-Mackensen, 2010).
Furthermore, Feest and Fikkert (2015) found that sensitivity to specific
kinds of mispronunciations develop at different ages depending on
language infants are learning. In other words, the native language
constraints which \emph{kinds} of mispronunciations infants are
sensitive to first, and that as infants develop, they become sensitive
to other mispronunciations. These studies award support to the
prediction that mispronunciation sensitivity increases with development.

Finally, some studies have found no difference in mispronunciation
sensitivity at different ages. Swingley and Aslin (2000) tested infants
over a wide age range of 5 months (18 to 23 months). They found that age
correlated with target fixations for both correct and mispronounced
labels, whereas the difference between the two (mispronunciation
sensitivity) did not. This suggests that as children develop, they are
more likely to look at the target in the presence of a correct or
mispronounced label, but that the difference between looks elicited by
the two conditions does not change. A similar response pattern has been
found for British English learning infants aged between 18 and 24 months
(Bailey \& Plunkett, 2002) as well as younger French-learning infants at
12 and 17 months (Zesiger, Lozeron, Levy, \& Frauenfelder, 2012). These
studies award support to the prediction that mispronunciation
sensitivity does not change with development.

Why would mispronunciation sensitivity change as infants develop, and
would it increase or decrease? The main hypotheses attribute change to
vocabulary growth. Both the Perceptual Attunement (Best, 1994, 1995) and
PRIMIR (Curtin \& Werker, 2007; Curtin et al., 2011; Werker \& Curtin,
2005) accounts situate a change in mispronunciation sensitivity
occurring along with an increase in vocabulary size, particularly with
the vocabulary spurt at about 18 months. As infants learn more words,
their focus shifts to the relevant phonetic dimensions needed for word
recognition. For example, an infant who knows a handful of words with
few phonological neighbors would not need to have fully specified
phonological representations in order to differentiate between these
words. As more phonologically similar words are learned, however, the
need for fully detailed phonological representations increases
(Charles-Luce \& Luce, 1995). Furthermore, a growing vocabulary also
reflects increased experience or familiarity with words, which may
sharpen the detail of their phonological representation (Barton, Miller,
\& Macken, 1980). If vocabulary growth leads to an increase in the
phonological specificity of infants' word representation, we should find
a relationship between vocabulary size and mispronunciation sensitivity.

Yet, the majority of studies examining a potential association between
mispronunciation sensitivity and vocabulary size have concluded that
there is no relationship (Bailey \& Plunkett, 2002; Ballem \& Plunkett,
2005; Mani \& Plunkett, 2007; Mani, Coleman, \& Plunkett, 2008;
Swingley, 2009; Swingley \& Aslin, 2000, 2002; Zesiger et al., 2012).
One notable exception comes from Mani and Plunkett (2010). Here,
12-month-old infants were divided into a low and high vocabulary group
based on median vocabulary size. High vocabulary infants showed greater
sensitivity to vowel mispronunciations than low vocabulary infants,
although this was not the case for consonant mispronunciations. Taken
together, although receiving considerable support from theories of
phono-lexical processing in language acquisition, there is very little
evidence for a role of vocabulary size in mispronunciation sensitivity.
In our current meta-analysis, we include the relationship between
mispronunciation sensitivity and vocabulary size to further disentangle
the disconnect between theory and experimental results.

In sum, the studies we have reviewed begin to paint a picture of the
development of infants' mispronunciation sensitivity. Each study
contributes one separate brushstroke and it is only by examining all of
them together that we can achieve a better understanding of the big
picture of early language development. Meta-analyses can provide unique
insights by estimating the population effect, both of infants' responses
to correct and mispronounced labels, and of their mispronunciations
sensitivity. Because we aggregate data over various age groups, this
meta-analysis can also investigate the role of maturation by assessing
the impact of age and vocabulary size. As a consequence, our results
will be important in evaluating theories and drive future research. We
also make hands-on recommendations for experiment planning, for example
by providing an effect size estimate for a priori power analyses
(Bergmann et al., 2018).

@@

\begin{longtable}{lllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:SummaryTable}Summary of all studies. Age is calculated by truncating the mean age reported in the paper. The abbreviations Comp and Prod refer to comprehension and production, respectively.}\\
\toprule
Paper & Publication format & Age & Vocabulary & N Effect Sizes\\
\midrule
Altvater-Mackensen (2010) & dissertation & 22, 25 & None & 13\\
Altvater-Mackensen et al. (2014) & paper & 18, 25 & None & 16\\
Bailey \& Plunkett (2002) & paper & 18, 24 & Comp & 12\\
Ballem \& Plunkett (2005) & paper & 14 & None & 4\\
Bergelson \& Swingley (2017) & paper & 6, 7, 9, 12 & None & 9\\
Bernier \& White (2017) & proceedings & 21 & None & 4\\
Delle Luche et al. (2015) & paper & 20, 19 & None & 4\\
Durrant et al. (2014) & paper & 19, 20 & None & 4\\
Höhle et al. (2006) & paper & 18 & None & 4\\
Højen et al. (n.d.) & gray paper & 19, 20 & Comp/Prod & 6\\
Mani \& Plunkett (2007) & paper & 15, 18, 24, 14, 20 & Comp/Prod & 14\\
Mani \& Plunkett (2010) & paper & 12 & Comp & 8\\
Mani \& Plunkett (2011) & paper & 23, 17 & None & 15\\
Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod & 4\\
Ramon-Casas \& Bosch (2010) & paper & 24, 25 & None & 4\\
Ramon-Casas et al. (2009) & paper & 21, 20, 43, 44 & Prod & 14\\
Ren \& Morgan (in press) & gray paper & 19 & None & 8\\
Renner (2017) & dissertation & 17, 24 & None & 6\\
Skoruppa et al. (2013) & paper & 23 & None & 5\\
Swingley (2003) & paper & 19 & Comp/Prod & 6\\
Swingley (2009) & paper & 17 & Comp/Prod & 4\\
Swingley (2016) & paper & 27, 28 & Prod & 9\\
Swingley \& Aslin (2000) & paper & 20 & Comp & 2\\
Swingley \& Aslin (2002) & paper & 15 & Comp/Prod & 4\\
Tamasi (2016) & dissertation & 30 & None & 4\\
Tao \& Qinmei (2013) & paper & 12 & None & 4\\
Tao et al. (2012) & paper & 16 & Comp & 6\\
van der Feest \& Fikkert, (2015) & paper & 24, 20 & None & 16\\
van der Feest \& Johnson (2016) & paper & 24 & None & 24\\
Wewalaarachchi et al. (2017) & paper & 24 & None & 8\\
White \& Aslin (2011) & paper & 18 & None & 4\\
White \& Morgan (2008) & paper & 18, 19 & None & 12\\
Zesiger \& Jöhr (2011) & paper & 14 & None & 8\\
Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod & 6\\
\bottomrule
\end{longtable}
\end{lltable}

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley and Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
removed 99 duplicate items and screened the remaining 299 items for
their title and abstract to determine whether each met the following
inclusion criteria: (1) original data was reported; (2) the experiment
examined familiar word recognition and mispronunciations; (3) infants
studied were under 31-months-of-age and typically developing; (4) the
dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{34}) consisted of 28
journal articles, 1 proceedings paper, 3 theses, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
provides an overview of all papers included in the present
meta-analysis.

@@

The 34 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Bergmann et al., 2018; Tsuji
et al., 2014). For each experiment (note that a paper typically has
multiple experiments), we entered variables describing the publication,
population, experiment design and stimuli, and results. For the planned
analyses to evaluate the development of mispronunciation sensitivity, we
focus on the following characteristics:

1 Condition: Were words mispronounced or not;\\
2 Mean age reported per group of infants, in days;\\
3 Vocabulary size, measured by a standardized questionnaire or list;

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 271 records in our data.

>>>>

@@

In a mature phono-lexical system, word recognition must balance
flexibility to slight variation (e.g., speaker identity, accented
speech) while distinguishing between phonological contrasts that
differentiate words in a given language (e.g.~cat-hat). The study of
Swingley and Aslin (2000) as well as subsequent studies examining
mispronunciation sensitivity probe this latter distinction. Phonological
contrasts relevant for the infant language-learner are determined by
their native language. For an infant learning Catalan, the vowel
contrast /e/-/E/ signifies a change in meaning, whereas this is not the
case for an infant learning Spanish. These contrasts are therefore not
inate, but must be learned. In this meta-analysis, we focus on infants'
developing ability to correctly apply the phonological distinctions for
their native language during word recognition. By aggregating all
publicly available evidence using meta-analysis, we can examine
developmental trends making use of data from a much larger and diverse
sample of infants than is possible in most single studies (see Frank et
al. (2017); for a notable exception). Before we outline the
meta-analytical approach and its advantages in detail, we first discuss
the proposals this study seeks to disentangle and the data supporting
each of the accounts.

Research following the seminal study by Swingley and Aslin (2000) has
extended mispronunciation sensitivity to infants as young as 8 to 10
months (Bergelson \& Swingley, 2017), indicating that from early stages
of the developing lexicon onwards, infants can and do detect
mispronunciations. Regarding the change in mispronunciation sensitivity
over development, however, only about half of studies have compared more
than one age group on the same mispronunciation task (see Table 1).
Across single studies all possible patterns of development lined out
above have been reported, making the current meta-analysis very
informative.

Several studies have found evidence for \emph{greater} mispronunciation
sensitivity as children develop. More precisely, the difference in
target looking for correct and mispronounced trials is reported to be
smaller in younger infants and grows as infants develop. Mani and
Plunkett (2007) tested 15-, 18-, and 24-month-olds learning British
English; although all three groups were sensitive to mispronunciations,
15-month-olds showed a less robust sensitivity. An increase in
sensitivity to mispronunciations has also been found from 20 to 24
months (Feest \& Fikkert, 2015) and 15 to 18 months (Altvater-Mackensen,
Feest, \& Fikkert, 2014) in Dutch infants, as well as German infants
from 22 to 25 months (Altvater-Mackensen, 2010). Furthermore, Feest and
Fikkert (2015) found that sensitivity to specific kinds of
mispronunciations develop at different ages depending on language
infants are learning. In other words, the native language constraints
which \emph{kinds} of mispronunciations infants are sensitive to first,
and that as infants develop, they become sensitive to other
mispronunciations.

Other studies have found no difference in mispronunciation sensitivity
at different ages. For example, Swingley and Aslin (2000) tested infants
over a wide age range of 5 months (18 to 23 months). They found that age
correlated with target fixations for both correct and mispronounced
labels, whereas the difference between the two (mispronunciation
sensitivity) did not. This suggests that as children develop, they are
more likely to look at the target in the presence of a correct or
mispronounced label, but that the difference between looks elicited by
the two conditions does not change. A similar response pattern has been
found for British English learning infants aged between 18 and 24 months
(Bailey \& Plunkett, 2002) as well as younger French-learning infants at
12 and 17 months (Zesiger, Lozeron, Levy, \& Frauenfelder, 2012).

One study has found evidence for infants to become \emph{less} sensitive
to mispronunciations as they develop. Mani and Plunkett (2011) presented
18- and 24-month-olds with mispronunciations varying in the number of
phonological features changed (e.g., changing an p into a b, a 1-feature
change, versus changing a p into a g, a 2-feature change). 18-month-olds
were sensitive to mispronunciations, regardless of the number of
features changed. 24-month-olds, in contrast, fixated the target image
equally for both correct and 1-feature mispronounced trials, although
they were sensitive to larger mispronunciations. In other words, for
1-feature mispronunciations at least, sensitivity decreased from 18 to
24 months.

Why would mispronunciation sensitivity change as infants develop?
Typically, a change in mispronunciation sensitivity is thought to occur
along with an increase in vocabulary size, particularly with the
vocabulary spurt at about 18 months. As infants learn more words, their
focus shifts to the relevant phonetic dimensions needed for word
recognition. For example, an infant who knows a handful of words with
few phonological neighbors would not need to have fully specified
phonological representations in order to differentiate between these
words. As more phonologically similar words are learned, however, the
need for fully detailed phonological representations increases
(Charles-Luce \& Luce, 1995). Furthermore, a growing vocabulary also
reflects increased experience or familiarity with words, which may
sharpen the detail of their phonological representation (Barton, Miller,
\& Macken, 1980). If vocabulary growth leads to an increase in the
phonological specificity of infants' word representation, we should find
a relationship between vocabulary size and mispronunciation sensitivity.

Yet, the majority of studies examining a potential association between
mispronunciation sensitivity and vocabulary size have concluded that
there is no relationship (Bailey \& Plunkett, 2002; Ballem \& Plunkett,
2005; Mani \& Plunkett, 2007; Mani, Coleman, \& Plunkett, 2008;
Swingley, 2009; Swingley \& Aslin, 2000, 2002; Zesiger et al., 2012).
One notable exception comes from Mani and Plunkett (2010). Here,
12-month-old infants were divided into a low and high vocabulary group
based on median vocabulary size. High vocabulary infants showed greater
sensitivity to vowel mispronunciations than low vocabulary infants,
although this was not the case for consonant mispronunciations. Taken
together, there is very little evidence for a role of vocabulary size in
mispronunciation sensitivity. In our current meta-analysis, we include
the relationship between mispronunciation sensitivity and vocabulary
size to better understand the variation in experimental results.

Although all mispronunciation sensitivity studies are generally
interested in the the phonological detail with which infants represent
familiar words, many studies pose more nuanced questions. These
questions concern issues at the intersection of phonological development
and lexical processing and often result in manipulations of the stimuli
and experimental procedure. Next to the core investigation of the shape
of development of infants' mispronunciation sensitivity, we take the
opportunity of a systematic aggregation of data to address these
questions and the influence of these manipulations on infants' ability
to detect mispronunciations and how this may change with development.

In designing their mispronunciation stimuli, Swingley and Aslin (2000)
chose consonant mispronunciations that were likely to confuse adults
(Miller \& Nicely, 1955). Subsequent research has settled on
systematically modulating phonemic features to achieve mispronunciations
of familiar words. By utilizing mispronunciations consisting of phonemic
changes, these experiments examine infants' sensitivity to factors that
change the identity of a word on a measurable level (i.e.~1-feature,
2-features, 3-features, etc.). The importance of controlling for the
degree of phonological mismatch, as measured by number of features
changed, is further highlighted by studies that find graded sensitivity
to both consonant (White \& Morgan, 2008) and vowel (Mani \& Plunkett,
2011) feature changes. The greater the number of features changed, or
\emph{mispronunciation size}, the easier it may be to detect a
mispronunciation, whereas more similar mispronunciations may be more
difficult to detect.

Although most research examining sensitivity to mispronunciations
follows a similar design, there are some notable differences. For
example, Swingley and Aslin (2000) presented infants with pairs of
familiar images, one serving as the labeled target and one as the
unlabeled distractor. In contrast, White and Morgan (2008; see also Mani
\& Plunkett, 2011; Skoruppa et al., 2013; Swingley, 2016) presented
infants with pairs of familiar (labeled target) and unfamiliar
(unlabeled distractor) objects. By using an unfamiliar object as a
distractor, the infant is presented with a viable option onto which the
mispronounced label can be applied (Halberda, 2003; Markman, Wasow, \&
Hansen, 2003). Infants ages 24 and 30 months associate a novel label
with an unfamiliar object, although only 30-month-olds retained this
label-object pairing (Bion, Borovsky, and Fernald, 2013). In contrast,
18-month-olds did not learn to associate a novel label with an
unfamiliar object, providing evidence that this ability is developing
from 18 to 30 months. We may find that if mispronunciation sensitivity
changes as children develop, that this change is modulated by
\emph{distractor familiarity}: whether the distractor used is familiar
or unfamiliar. Although mispronunciation sensitivity in the presence of
a familiar compared to unfamiliar distractor has not been directly
compared, the baseline preference for familiar compared to novel stimuli
is also thought to change as infants develop (Hunter \& Ames, 1988).
Furthermore, young children have been found to look longer at objects
for which they know the name, compared to objects of an unknown name
(Schafer \& Plukett, 1998). In other words, in absentia of a label,
infants may be more or less likely to fixate on an unfamiliar object. To
account for inherent preferences to the target or distractor image,
mispronunciation experiments typically compare the increase in fixations
to the target image from a silent baseline to post-labeling or present
the same yoked pairs of target and distractor images in in both a
correct and mispronounced labelling context. Considering this evidence,
we may expect that in older, but not younger, children, the presence of
an unfamiliar distractor may lead to greater mispronunciation
sensitivity than in the presence of a familiar distractor.

Furthermore, when presenting infants with a familiar distractor image,
some studies control the \emph{phonological overlap between target and
distractor labels}. For example, when examining sensitivity to a
mispronunciation of the target word \enquote{dog}, the vowel
mispronunciation \enquote{dag} would be paired with a distractor image
that shares onset overlap, such as \enquote{duck}. This ensures that
infants can not use the onset of the word to differentiate between the
target and distractor images (Fernald, Swingley, \& Pinto, 2001).
Instead, infants must pay attention to the mispronounced phoneme in
order to successfully detect the change. The influence of distractor
overlap also depends on the \emph{position of mispronunciation} in the
word, which can be at word onset, medial, or final positions. Models of
spoken word processing place more or less importance on the position of
a phoneme in a word. The COHORT model (Marslen-Wilson \& Zwitserlood,
1989) describes lexical access in one direction, with the importance of
each phoneme decreasing as its position comes later in the word. In
contrast, the TRACE model (McClelland \& Elman, 1986) describes lexical
access as constantly updating and reevaluating the incoming speech input
in the search for the correct lexical entry, and therefore can recover
from word onset and to a lesser extent medial mispronunciations.

TRACE has also been used to model infants' sensitivity to
mispronunciation position (Mayor \& Plunkett, 2014), finding that as
lexicon size increases, so does sensitivity to onset mispronunciations,
whereas medial mispronunciations do not experience similar growth. In
early language acquisition, infants typically know more consonant
compared to vowel onset words. When tested on their recognition of
familiar words, therefore, younger infants would show greater
sensitivity to onset mispronunciations, which are frequently consonant
mispronunciations. The prevalence of consonant onset words may
contribute to the finding that consonants carry more weight in lexical
processing (C-bias; see Nazzi, Poltrock, \& Von Holzen, 2016 for a
recent review). In mispronunciation sensitivity, this would translate to
consonant mispronunciations impairing word recognition to a greater
degree than vowel mispronunciations. Yet, the handful of studies
directly comparing sensitivity to consonant and vowel mispronunciations
mostly find symmetry as opposed to an asymmetry between consonants and
vowels. English-learning 12-, 15-, 18-, and 24-month-olds (Mani \&
Plunkett, 2007; 2010 keps and tups) and Danish-learning 20-month-olds
(Hojen et al., unpublished) demonstrate similar sensitivity to consonant
and vowel mispronunciations. One study did find weak evidence for
greater sensitivity to consonant compared to vowel mispronunciations
(Swingley, 2016). The English-learning infants tested by Swingley were
older than previous studies (mean age 28 months). In word learning, the
C-bias has been found to develop later in English learning infants
(Floccia, Nazzi, Delle Luche, Poltrock, \& Goslin, 2014; Nazzi, Floccia,
Moquet, \& Butler, 2009). In the current meta-analysis, we attempt to
synthesize studies examining sensitivity to the \emph{type of
mispronunciation}, whether consonant or vowel, across different ages to
determine whether infants generally exhibit more sensitivity to
consonant compared to vowel mispronunciations in familiar word
recognition as predicted by a learned account of C-bias emergence
(Floccia et al., 2014; Keidel et al., 2007; Nazzi et al., 2016). We
further examine the impact of language family on mispronunciation
sensitivity to consonants and vowels, as C-bias emergence has been found
to have a different developmental trajectory for Romance (French,
Italian) compared to Germanic (British English, Danish) languages (Nazzi
et al., 2016).

Finally, mispronunciation sensitivity in infants has been examined in
many different languages, such as English, Spanish, French, Dutch,
German, Catalan, Danish, and Mandarin Chinese (see Table 1). Infants
learning different languages have different ages of acquisition for
words in their early lexicon, leaving direct comparisons between
languages within the same study difficult and as a result rare. Although
we do not explicitly compare overall mispronunciation sensitivity by
language (although see previous paragraph for rationale to test by
language family), we assess evidence of mispronunciation sensitivity
from many different languages using a meta-analytic approach.

In sum, the studies we have reviewed begin to paint a picture of the
development of infants' mispronunciation sensitivity. Each study
contributes one separate brushstroke and it is only by examining all of
them together that we can achieve a better understanding of the big
picture of early language development. Meta-analyses can provide unique
insights by estimating the population effect, both of infants' responses
to correct and mispronounced labels, and of their mispronunciations
sensitivity. Because we aggregate data over various age groups, this
meta-analysis can also investigate the role of maturation by assessing
the impact of age and vocabulary size. We also make hands-on
recommendations for experiment planning, for example by providing an
effect size estimate for a priori power analyses (Bergmann et al.,
2018).

@@

\scriptsize{
\begin{longtable}{llllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:SummaryTable}Summary of all studies. Age: truncation of mean age reported in the paper. Vocabulary: Comp = comprehension, Prod = production. Distractor Familiarity: Fam = Familiar Distractor, Unfam = Unfamiliar Distractor. Distractor Target Overlap: position of overlap between target and distractor; O = onset, M = medial, C = coda. Mispronunciation Size: number of features changed; commas indicate when sizes were compared separately (e.g. 1, 2, 3), dashes indicate the range of sizes were aggregated (e.g. 1-3). Mispronunciation Position: O = onset, M = medial, C = coda. Mispronunciation Type: C = consonant, V = vowel, T = tone. For both Mispronunciation Position and Type, a slash separator indicates that is was tested but a distinction was not made in the stimuli. For all categories, unspec. indicates that the value was unspecified in the paper}\\
\toprule
 &  &  &  & \multicolumn{1}{c}{Distractor} & & \multicolumn{3}{c}{Mispronunciation}  &\\
\cmidrule(r){5-5} \cmidrule(r){7-9}
Paper & Format & Age & Vocabulary & Familiarity & Target Overlap & Size & Position & Type & N Effect Sizes\\
\midrule
Altvater-Mackensen (2010) & dissertation & 22, 25 & None & fam, unfam & O, novel & 1 & O, O/M & C & 13\\
Altvater-Mackensen et al. (2014) & paper & 18, 25 & None & fam & O & 1 & O & C & 16\\
Bailey \& Plunkett (2002) & paper & 18, 24 & Comp & fam & none & 1, 2 & O & C & 12\\
Bergelson \& Swingley (2017) & paper & 7, 9, 12, 6 & None & fam & none & unspec & O/M & V & 9\\
Bernier \& White (2017) & proceedings & 21 & None & unfam & novel & 1, 2, 3 & O & C & 4\\
Delle Luche et al. (2015) & paper & 20, 19 & None & fam & O & 1 & O & C/V & 4\\
Durrant et al. (2014) & paper & 19, 20 & None & fam & O & 1 & O & C/V & 4\\
Höhle et al. (2006) & paper & 18 & None & fam & none & 1 & O & C & 4\\
Højen et al. (n.d.) & gray paper & 19, 20 & Comp/Prod & fam & C, O & 2-3 & O/M, C/M & C/V, V, C & 6\\
Mani \& Plunkett (2007) & paper & 15, 18, 24, 14, 20 & Comp/Prod & fam & O & 1-2, 1 & O & V, C/V, C & 14\\
Mani \& Plunkett (2010) & paper & 12 & Comp & fam & O & 1 & M, O & V, C & 8\\
Mani \& Plunkett (2011) & paper & 23, 17 & None & unfam & novel & 1-3, 1, 2, 3 & M & V & 15\\
Mani, Coleman, \& Plunkett (2008) & paper & 18 & Comp/Prod & fam & O & 1 & M & V & 4\\
Ramon-Casas \& Bosch (2010) & paper & 24, 25 & None & fam & none & unspec & M & V & 4\\
Ramon-Casas et al. (2009) & paper & 21, 20 & Prod & fam & none & unspec & M & V & 10\\
Ren \& Morgan (in press) & gray paper & 19 & None & unfam & none & 1 & O, C & C & 8\\
Skoruppa et al. (2013) & paper & 23 & None & unfam & O/M & 1 & C & C & 4\\
Swingley (2003) & paper & 19 & Comp/Prod & fam & O & 1 & O, M & C & 6\\
Swingley (2009) & paper & 17 & Comp/Prod & fam & none & 1 & O, C & C & 4\\
Swingley (2016) & paper & 27, 28 & Prod & unfam & novel & 1 & O/M & C/V, C, V & 9\\
Swingley \& Aslin (2000) & paper & 20 & Comp & fam & none & 1 & O & C/V & 2\\
Swingley \& Aslin (2002) & paper & 15 & Comp/Prod & fam & none & 1, 2 & O/M & C/V & 4\\
Tamasi (2016) & dissertation & 30 & None & unfam & novel & 1, 2, 3 & O & C & 4\\
Tao \& Qinmei (2013) & paper & 12 & None & fam & none & unspec & unspec & T & 4\\
Tao et al. (2012) & paper & 16 & Comp & fam & none & unspec & unspec & T & 6\\
van der Feest \& Fikkert, (2015) & paper & 24, 20 & None & fam & O & 1 & O & C & 16\\
van der Feest \& Johnson (2016) & paper & 24 & None & fam & O & 1 & O & C & 20\\
Wewalaarachchi et al. (2017) & paper & 24 & None & unfam & novel & 1 & O/M/C & C/V/T, V, C, T & 8\\
White \& Aslin (2011) & paper & 18 & None & unfam & novel & 1 & M & V & 4\\
White \& Morgan (2008) & paper & 18, 19 & None & unfam & novel & 1, 2, 3 & O & C & 12\\
Zesiger \& Jöhr (2011) & paper & 14 & None & fam & none & 1 & O, M & C, V & 7\\
Zesiger et al. (2012) & paper & 12, 19 & Comp/Prod & fam & none & 1, 2 & O & C & 6\\
\bottomrule
\end{longtable}
\end{lltable}

We first generated a list of potentially relevant items to be included
in our meta-analysis by creating an expert list. This process yielded
110 items. We then used the google scholar search engine to search for
papers citing the original Swingley and Aslin (2000) publication. This
search was conducted on 22 September, 2017 and yielded 288 results. We
removed 99 duplicate items and screened the remaining 299 items for
their title and abstract to determine whether each met the following
inclusion criteria: (1) original data was reported; (2) the experiment
examined familiar word recognition and mispronunciations; (3) infants
studied were under 31-months-of-age and typically developing; (4) the
dependent variable was derived from proportion of looks to a target
image versus a distractor in a eye movement experiment; (5) the stimuli
were auditory speech. The final sample (n = \emph{32}) consisted of 27
journal articles, 1 proceedings paper, 2 theses, and 2 unpublished
reports. We will refer to these items collectively as papers. Table 1
provides an overview of all papers included in the present
meta-analysis.

@@

The 32 papers we identified as relevant were then coded with as much
consistently reported detail as possible (Bergmann et al., 2018; Tsuji
et al., 2014). For each experiment (note that a paper typically has
multiple experiments), we entered variables describing the publication,
population, experiment design and stimuli, and results. For the planned
analyses to evaluate the development of mispronunciation sensitivity and
modulating factors, we focus on the following characteristics:

1 Condition: Were words mispronounced or not;\\
2 Mean age reported per group of infants, in days;\\
3 Vocabulary size, measured by a standardized questionnaire or list;\\
4 Size of mispronunciation, measured in features changed;\\
5 Distractor familiarity: familiar or unfamiliar;\\
6 Phonological overlap between target and distractor: onset,
onset/medial, rhyme, none, novel word;\\
7 Position of mispronunciation: onset, medial, offset, or mixed;\\
8 Type of mispronunciation: consonant, vowel, or both.

We separated conditions according to whether or not the target word was
mispronounced to be able to investigate infants' looking to the target
picture as well as their mispronunciation sensitivity, which is the
difference between looks to the target in correct and mispronounced
trials. When the same infants were further exposed to multiple
mispronunciation conditions and the results were reported separately in
the paper, we also entered each condition as a separate row (e.g.,
consonant versus vowel mispronunciations; Mani \& Plunkett, 2007). The
fact that the same infants contributed data to multiple rows (minimally
those containing information on correct and mispronounced trials) leads
to shared variance across effect sizes, which we account for in our
analyses (see next section). We will call each row a record; in total
there were 251 records in our data.
